--- 
title: "In Search of Lost Emotions"
author: "MohammadHossein Manuel Haqiqatkhah"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [packages.bib] #book.bib
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Preface

This document is the report of my internship at KU Leuven's Quantitative Psychology and Individual Differences Research Group in the academic year 2018-2019.

I start Chapter \@ref(intro) with an introduction and elaborate the research questions, methods, research material, and a short overwies of the following chapters. I also discuss how the goal of the internship evolved over time and how it differed from the initial intentions.
Then I move on to Chapter \@ref(pca) the first round of analyses, namely principal component analysis (PCA), and report the results.
Later in Chapter \@(irt) I introduce item response theory (IRT) and discuss the outcomes of the premilinary explorations via IRT.
Then, Chapter \@(mirt) addresses multi-dimensional IRT modeling which yields to multi-dimensional constructs for emotions.
In Chapter \@(fa) I apply exploratory-confirmatory factor analysis (E/CFA) and put th
In Chapter \@(sem) I model measurement errors and 
...

In Appendix \@(esmclass) appendices I include the reproducible R scripts used for this project.


This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages

```
